Shared Characterizations of Challenging Demands and Job Resources across O*NET Element Classifications

### 2025-12-02 Submission.Rmd
Making minor edits

csl               : "sage-harvard.csl"
documentclass     : "apa7" #interact
classoption       : "man"
output: 
  papaja::apa6_pdf:
    latex_engine: xelatex 
---

@@

```{r demos}

@@

attention$id <- 1:nrow(attention) #adds unique identifier to satisfy inane requirement of classify_occupation()

ISCO <- classify_occupation(attention, text_col = 'item400', isco_level = 1)

>>>>

csl               : "apa7.csl"
documentclass     : "apa7" #interact
classoption       : "man"
output: 
  papaja::apa6_pdf:
    latex_engine: xelatex 
---

@@

```{r demos, eval=FALSE}

@@

attention$id <- 1:nrow(attention) #adds unique identifier to satisfy inane requirement of classify_occupation()
R.version
ISCO <- classify_occupation(attention, text_col = 'item400', isco_level = 1)
